\section{Related Work and Conclusion}\label{sec:relatedconclusions}

\paragraph{Related work.}
Existing \jvm cache libraries---Guava~\cite{guava}, Caffeine~\cite{caffeine} (which implements W-TinyLFU~\cite{einziger2017tinylfu}), Spring Cache~\cite{spring_cache}, and function-level wrappers~\cite{javamemoization}---either require explicit wrapper code at every call site, depend on a container framework, or force callers to hold a functional reference, and none are usable as an \emph{in-place} refactoring target for an automated tool. Memoization combinators in adjacent ecosystems make the same point: Clojure's \code{clojure.core.memoize}~\cite{clojure_core_memoize} and Scala's function-level idioms~\cite{scala_memo} both wrap an existing functional value rather than rewriting a method in place, and Acar's self-adjusting computation~\cite{acar_sac} generalises memoization but requires a bespoke programming model---none retrofit to an existing \jvm class without touching call sites. Bytecode-transformation libraries for cross-cutting concerns have a long history (AspectJ~\cite{aspectj}; \agp's instrumentation \api~\cite{agp_instrumentation}), and MemoizeLib's class visitor can be viewed as a purpose-built aspect weaver for a single aspect. The prior work most adjacent to ours is iMMutator~\cite{immutator}, which identifies memoization candidates in \jvm code with high precision but stops short of emitting correct caching code; \llm-driven performance refactoring~\cite{llm_refactoring,hall_costa} hits the same wall. MemoizeLib is explicitly designed to serve as the downstream target that closes it: a detector can emit an annotation patch rather than a wrapper-code patch, which collapses the correctness-heavy part of the refactoring into a directly tractable one.

\paragraph{Why no head-to-head benchmark.} A direct comparison against Guava or Caffeine is intentionally out of scope for this tool-demo version: their builder-centric APIs require manual wrapping of every target method, so any benchmark would compare two fundamentally different integration models---an in-place rewrite against a hand-written wrapper---rather than two caches on common ground. A controlled head-to-head is earmarked as future work.

\paragraph{Conclusion and artefact.}
\textbf{MemoizeLib} is an annotation-driven, cross-platform memoization library designed to serve as the drop-in refactoring target for automated detectors and \llm-driven refactoring tools. A three-annotation API collapses the correctness burden behind a declarative boundary; a build-time bytecode transform rewrites annotated methods in place on both Android and the plain \jvm; and a zero-dependency runtime provides three eviction policies (\lru, \fifo, \lfu) plus an unbounded mode, \ttl, auto-monitor, and embedded observability whose disabled-state cost is derived in Section~\ref{sec:tool}. A Jetpack Benchmark harness over ten overlapping-subproblem algorithms, released together with the library as an open research artefact, quantifies the per-algorithm speedup, per-policy hot-path cost, and hit-rate break-even. \emph{Future work} includes (i)~a head-to-head against Guava and Caffeine, (ii)~integration with an iMMutator-style detector, and (iii)~the full device campaign populating the \pending{} cells. The library, the harness, the Sphinx documentation, and the \LaTeX{} source of this paper are available at
% TODO: replace with real anonymised repository before submission
\url{https://anonymous.4open.science/r/memoize-lib} (anonymised for review).
